Does It Scale? Static Output Approximation of PHP Web Applications Using Symbolic Execution

### 2017-01-14 paper.tex
monochromatic diagrams

@@

\definecolor{lightgrey}{HTML}{CCFFEE}

@@

\subsection{Measuring Approximation Success} \label{heuristic}
In order to accurately answer the question how good our symbolic execution
engine approximates client page output, we would require knowledge of all
possible variants to compare our approximation against. Since we do not have
any ground truth information alike, we approach this demand by using a
heuristic. Rather than having knowledge about all client page output variants
we say our approximation is sound if all string literals (which are embedded in
and  scattered across server-side code) that may eventually become part of any
client page output variant (in the following referred to as \emph{output
candidate}) is contained in our symbolic output approximation.
It is non-trivial to determine whether a string literal is an output candidate,
so we heuristically classify string literals as output candidates if they
contain the characters \tt{<}, \tt{>}, or both since we expect output to contain
HTML tags.

@@

\subsection{Measuring Approximation Accuracy}
\label{HowAccurateIsOurApproximation} 
In Section \ref{heuristic} we introduced the definition of output candidates as
expected output. As a most accurate approximation contains all output
candidates, we define two metrics to measure accuracy of our approximation.

First, we measure how much of the expected output was actually processed by the
symbolic interpreter.  Once a line of code, a statement or expression
containing an output candidate is actually an element in an execution path, we
define this output candidate as reached. We define the metric \emph{reach
coverage} as the ratio of output candidates that are reached and the total
number of output candidates in the analyzed system. Although a reached output
candidate is processed by the symbolic interpreter, it does not guarantee we
will see that output candidate in the symbolic output. Second, we define the
metric \emph{output coverage} as the ratio of output candidates that are
contained in the output of the symbolic interpreter and the total number of
output candidates in the analyzed system.  For an imprecise approximation, we
may see loss of output candidate information resulting in a output coverage
lower than the reach coverage.

The coverage results are illustrated in Figure \ref{coverage}. We could
replicate high coverage results for the four small-scale systems with a reach
coverage and output coverage over 80 percent respectively. For the three
modern/large-scale systems we measured poor coverage with reach coverage
ranging from 5 to 30 percent and output coverage ranging from 4 to 20 percent.
We measured medium to high coverage for the more recent small-scale systems:
reach coverage ranging from 43 to 85 percent, output coverage ranging from 40
to 85 percent.

>>>>

\usepackage{tikz}
\usetikzlibrary{patterns}

@@

\definecolor{lightgrey}{HTML}{FFFFFF}

@@

\subsection{Measuring Approximation Success} \label{heuristic}
In order to accurately answer the question how good our symbolic execution
engine approximates client page output, we would require knowledge of all
possible variants to compare our approximation against. Since we do not have
any ground truth information alike, we approach this demand by using a
heuristic. Rather than having knowledge about all client page output variants
we say our approximation is accurate if all string literals (which are embedded
in and  scattered across server-side code) that may eventually become part of any
client page output variant (in the following referred to as \emph{output
candidate}) is contained in our symbolic output approximation.
It is non-trivial to determine whether a string literal is an output candidate,
so we heuristically classify string literals as output candidates if they
contain the characters \tt{<}, \tt{>}, or both since we expect output to contain
HTML tags.

@@

\subsection{Measuring Approximation Accuracy}
\label{HowAccurateIsOurApproximation} 
In Section \ref{heuristic} we introduced the definition of output candidates as
expected output. For an approximation to be most accurate, it needs to contain
all output candidates of a system analyzed. Based on whether output
candidates are reached by an execution path and part of the output
approximatiopn define two metrics to approach measuring accuracy.

We measure how much of the expected output was actually processed by the
symbolic interpreter.  Once a line of code, a statement or expression
containing an output candidate is actually an element in an execution path, we
define this output candidate as \emph{reached}. We define the metric \emph{reach
coverage} as the ratio of output candidates that are reached and the total
number of output candidates in the analyzed system. Although a reached output
candidate is processed by the symbolic interpreter, it does not guarantee we
will see that output candidate in the symbolic output. Therefore, we define the
metric \emph{output coverage} as the ratio of output candidates that are
contained in the output of the symbolic interpreter and the total number of
output candidates in the analyzed system.  
%For an imprecise approximation, we may see loss of output candidate information
% resulting in a output coverage lower than the reach coverage.

The coverage results for our case study are illustrated in Figure
\ref{coverage}. We could replicate high coverage results for the four small-scale systems with a reach
coverage and output coverage over 80 percent respectively. For the three
modern/large-scale systems we measured poor coverage with reach coverage
ranging from 5 to 30 percent and output coverage ranging from 4 to 20 percent.
We measured medium to high coverage for the more recent small-scale systems:
reach coverage ranging from 43 to 85 percent, output coverage ranging from 40
to 85 percent.
